Title

### 2019-05-01 4_method.tex
expand thinking on method

@@

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\end{subfigure}
\caption{The equidistant points between a vert and a line form a parabola. There are different methods for generating toolpaths which are in between the medial axis and the outline.}
\label{medial_axis_parabolas}
\end{figure}

\subsection{Angle of fingers introduced on the skeleton}
\Cref{finger_angles}
Cannot be optimized.
Always has to be orthogonal to the polygon segment.
Otherwise the algorithm isn’t stable w.r.t. extra vertices.

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\end{subfigure}
\caption{Figner angles should always be orthogonal}
\label{finger_angles}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
\end{subfigure}
\caption{We can do single-bead segments. Blue is travel move.}
\label{single_bead_strategy}
\end{figure}

@@

\subsection{Where to add fingers?}
\Cref{rounded_dist_measures}
Based on unrounded distance measures.
Otherwise we don’t get the switch to twice the bead width
Moreover, the algorithm wouldn’t be stable: the locations where bones would get introduces would depend on where the other joints are, instead of on the distance measure.

\hl{But what does this mean?
When should I round distances to integer multiples?!}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/rounded_dist_measures.jpg}
\caption{Distance measure rounding}
\label{rounded_dist_measures}
\end{figure}

>>>>

\begin{figure}[H]
\begin{subfigure}{0.9\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
\end{subfigure}
\begin{subfigure}{0.9\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
\label{medial_axis_parabolas_functions}
\end{subfigure}
\caption{The equidistant points between a vert and a line form a parabola. There are different methods for generating toolpaths which are in between the medial axis and the outline. Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
\label{medial_axis_parabolas}
\end{figure}

@@

Perhaps we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
No, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!

\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/angular_based_spacing.pdf}
\caption{Angular based spacing isn't feasible. The bottom medial axis bone has different spacing based on the two patches. The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
\label{angular_based_spacing}
\end{figure}

\subsection{Angle of fingers introduced on the skeleton}
\Cref{finger_angles}
Cannot be optimized.
Always has to be orthogonal to the polygon segment.
Otherwise the algorithm isn't stable w.r.t. extra vertices.

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\caption{Stability against extra vertices}
\label{finger_angles_stability}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\end{subfigure}
\caption{Figner angles should always be orthogonal}
\label{finger_angles}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
\end{subfigure}
\caption{We can do single-bead segments. Blue is travel move.}
\label{single_bead_strategy}
\end{figure}

@@

%\subsection{Where to add fingers?}
%\Cref{rounded_dist_measures}
%Based on unrounded distance measures.
%Otherwise we don't get the switch to twice the bead width.
%Moreover, the algorithm wouldn't be stable: the locations where bones would get introduces would depend on where the other joints are, instead of on the distance measure.
%\hl{But what does this mean?
%When should I round distances to integer multiples?!}

\subsection{Angle estimation}
When the angle between two outline segments is small, the naive method will produce long triangular cusps.
We can measure the angle between two outline segments which generate a MAT segment by looking at the angle where the lines going through those segments (would) meet.
Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
if the Euclidean distance is larger than twice the distance measure difference, the angle between the segments is less than {\SI{60}{\degree}}.

\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{Distance based angle estimation. By comparing the euclidean distance between two vertices with the distance measure of the MAT we can skip comparing the angles between the outline segments.}
\label{distance_based_angles}
\end{figure}

The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices:t
\begin{figure}[H]
\centering
\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
\end{figure}

\subsection{Where to round distance measures?}
\Cref{rounded_dist_measures}
Based on where the medial axis stops being of high curvature.

We mark bones as to-be-split based on the angle between the two edges of the polygon for which this bone is the bisector.
Parabolas are always to-be-split, since all points on the parabola are equidistant, so not rounding would introduce a gap along the parabola.
%For parabolas we check the angle between the three points involved: the end points of the line segment and the point which together generate the parabola. That angle is never less than \SI{90}{\degree}.

\hl{Is it impossible for three marked edges to come together?}

When a vertex in the medial axis has only a part of the connected bones marked then the distance measure should be rounded?
But that isn't stable against perturbations such as \cref{finger_angles_stability}!

\begin{figure}[H]
\centering
\includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
\caption{Distance measure rounding}
\label{rounded_dist_measures}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\columnwidth]{sources/method/rounded_vs_unrounded.pdf}
\caption{Toolpaths employing dist rounding vs without.}
\label{rounded_vs_unrounded}
\end{figure}
